---
title: "Comparison of datasets"
output: html_notebook
---

```{r}
rm(list=ls())
```

```{r}
library(compareDF)
library(htmlTable)
library(janitor)
```

First read the new data.

```{r}
new_data_path <- "../sent_to_Aditya_02092020/"
new_dyad <- read.csv(paste0(new_data_path, "HPV_dyad_2019-12-16.csv"))
new_dt <- read.csv(paste0(new_data_path, "aditya_hpv_final_v3_attributes_referred_by_final.csv"), as.is = T)
```

Next read the old data. 


```{r}
old_dt <- read.csv("../Aditya_11032019/dataset_used for create_dataset_HPV1 & extract_dyad/houston_hpv.csv", as.is = T)
```

Compare the two datasets:
The new dataset has dimensions `r dim(new_dt)` rows and the dimensions of the old dataset are `r dim(old_dt)`. T

Convert the column names in both data frames to lower case to make a comparison:
```{r}
library(data.table)
setnames(old_dt, tolower(names(old_dt)))
setnames(new_dt, tolower(names(new_dt)))
```

Now compare the columns in the two datasets:

```{r}
compare_df_cols(old_dt, new_dt)
```

And lets compare some specific columns of interest in the two datasets:
```{r}
summary(old_dt$hr_16)
summary(new_dt$hr_16)

summary(old_dt$hr_18)
summary(new_dt$hr_18)

summary(old_dt$hr_45)
summary(new_dt$hr_45)
```